### 2021-01-29 README.Rmd
incorporated simon's suggestions

We present an example analysis using toy data pre-loaded into the package.

```{r}
library(tidyverse)
library(forestecology)
library(sf)
library(sfheaders)
library(blockCV)
library(yardstick)
library(snakecase)
library(patchwork)
library(tidyr)
```

@@

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex,
    census_2 = census_2_ex %>% filter(!str_detect(codes, "R")),
    id = "ID"
    ) %>%
  mutate(sp = snakecase::to_any_case(sp) %>% factor())
```

@@

Next we add information pertaining to our spatial cross-validation scheme. We first manually define the spatial blocks that will act as our cross-validation folds and convert them to an `sf` object.

@@

blocks_ex <- bind_rows(
  sfheaders::sf_polygon(fold1),
  sfheaders::sf_polygon(fold2)
) %>%
  mutate(folds = c(1, 2) %>% factor())
```

@@

```{r}
focal_vs_comp_ex %>%
  yardstick::rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

We present an example analysis using toy data pre-loaded into the package where we will

1. Compute growth of trees based on census data
1. Add spatial information
1. Compute focal versus competitor tree information
1. Fit model and make predictions
1. Run spatial cross-validation

```{r}
library(tidyverse)
library(forestecology)
library(blockCV)
library(patchwork)
```

@@

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex,
    census_2 = census_2_ex %>% filter(!str_detect(codes, "R")),
    id = "ID"
    ) %>%
  mutate(sp = to_any_case(sp) %>% factor())
```

@@

Next we add information pertaining to our spatial cross-validation scheme. We first manually define the spatial blocks that will act as our cross-validation folds and convert them to an `sf` object using the `sf_polygon()` function from the `sfheaders` package.

@@

blocks_ex <- bind_rows(
  sf_polygon(fold1),
  sf_polygon(fold2)
) %>%
  mutate(folds = c(1, 2) %>% factor())
```

@@

```{r}
focal_vs_comp_ex %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```
